Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-01-06 reports/rmarkdown/manuscript/manuscript_template.Rmd
updates manuscript

```{r, echo = FALSE, eval = TRUE}
# Load reasult from the analysis
metadata <- read.csv2("../../../results/metadata_integration.csv",row.names = 1)
patient_groups <- metadata$group_M4_CVLv3
bac_communities <- as.matrix(read.csv2("../../../results/bacterial_communities.csv",row.names = 1))[,1]
SNN_patients <- read.csv("../../../results/patient_SNN_graph.csv",row.names = 1)
SNN_bacteria <- read.csv("../../../results/bacteria_SNN_graph.csv",row.names = 1)
clean_Ftest <- read.csv2("../../../results/metadata_association_results.csv",row.names = 1)
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")

@@

```{r, echo = FALSE, eval = TRUE , fig.asp=9/10}
# Define Layout and set labels
layout(matrix(c(1,1,1,1,      3,3,3,3,          3,4,4,4,
                2,2,2,2,      3,3,3,3,          3,5,5,5,
                6,6,6,6,      9,9,9,9,          9,9,9,9,
                7,7,7,7,     10,10,10,10,     10,10,10,10,
                8,8,8,8,     10,10,10,10,     10,10,10,10 ) , ncol= 12,byrow = T),
       widths = 1,heights = c(1,1,.7,.7,.7))
# layout.show(29)
figlabels <- letters

@@

par(mar=c(0,0,0,0))
plot( g , vertex.label.cex=0.000001 , vertex.color = pal[factor(metadata$joint_clustering)] ,
      edge.width=  ( E(g)$weight / max(E(g)$weight)) ,
      vertex.size=10,main="", 
      edge.color=colorRampPalette(c("grey95","black"))(90) [ round( E(g)$weight / max(E(g)$weight) * 88 )+1 ] )
legend("topright",title.adj = 0,
       legend = levels(factor(metadata$joint_clustering)),xjust = 0,yjust = 1,
       bty = "n",pch = 21,pt.bg = pal,pt.cex = 1,xpd=T)

@@

barlist( data = rbind(  BV=mL ,
                        counts_16S=xL),
         main = "Lactobacillus",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)

@@

barlist( data = rbind(  BV=mM ,
                        counts_16S=xM),
         main = "Monbilicus",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)

barlist( data = rbind(  BV=mG ,
                        counts_16S=xG),
         main = "Gardanerella",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)

@@

shann <- vegan::diversity(t(x),index = c("shannon") )
simp <- vegan::diversity(t(x),index = c("simpson") )
invsimp <- vegan::diversity(t(x),index = c("invsimpson") )
divers <- as.matrix(rbind(shann,simp,invsimp) )
divers[is.infinite(divers)] <- 0
rownames(divers) <- c("Shannon","simpson","Inv Simpson")
barlist( data = divers,
         main = "",
         genes = c("Shannon","simpson","Inv Simpson"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)

@@

###################################
# BACTERIAL VAGINOSIS COMPARISSON #
###################################
par(mar=c(4,5,1,12))
temp <- t(t(2^x-1)/colSums(2^x-1))
taxa <- read.csv2("../../../results/taxonomy.csv",row.names = 1,stringsAsFactors = F,as.is = T)
taxa[is.na(taxa)] <- "NA"
taxa <- taxa[rownames(temp),]
temp <- rowsum(temp , taxa$Class)
temp[is.nan(temp)] <- 0
o <- order( rowSums(temp) , decreasing = T)
sample_o <- order( metadata$joint_clustering )
temp <- temp[o,sample_o]*100
temp <- temp[-grep("NA",rownames(temp)),]
temp <- rbind(temp[1:16,], Other = colSums(temp[17:nrow(temp),]) )

>>>>

```{r, echo = FALSE, eval = TRUE}
# Load reasult from the analysis
metadata <- read.csv2("../../../results/metadata_integration.csv",row.names = 1)
patient_groups <- metadata$joint_clustering
bac_communities <- as.matrix(read.csv2("../../../results/bacterial_communities.csv",row.names = 1))[,1]
SNN_patients <- read.csv("../../../results/patient_SNN_graph.csv",row.names = 1)
SNN_bacteria <- read.csv("../../../results/bacteria_SNN_graph.csv",row.names = 1)
clean_Ftest <- read.csv2("../../../results/metadata_association_results.csv",row.names = 1)
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")

@@

```{r, echo = FALSE, eval = TRUE , fig.asp=9/10}
# Define Layout and set labels
layout(matrix(c(1,1,1,1,      3,3,3,3,          3,4,4,4,
                2,2,2,2,      3,3,3,3,          3,5,5,5,
                6,6,6,6,      9,9,9,9,          9,9,9,9,
                7,7,7,7,     10,10,10,10,     10,10,10,10,
                8,8,8,8,     10,10,10,10,     10,10,10,10 ) , ncol= 12,byrow = T),
       widths = 1,heights = c(1,1,.7,.7,.7))
# layout.show(12)
figlabels <- letters

@@

par(mar=c(0,0,0,0))
plot( g , vertex.label.cex=0.000001 , vertex.color = pal[factor(patient_groups)] ,
      edge.width=  ( E(g)$weight / max(E(g)$weight)) ,
      vertex.size=10,main="", 
      edge.color=colorRampPalette(c("grey95","black"))(90) [ round( E(g)$weight / max(E(g)$weight) * 88 )+1 ] )
legend("topright",title.adj = 0,
       legend = levels(factor(patient_groups)),xjust = 0,yjust = 1,
       bty = "n",pch = 21,pt.bg = pal,pt.cex = 1,xpd=T)

@@

barlist( data = rbind(  BV=mL ,
                        counts_16S=xL),
         main = "Lactobacillus",
         genes = c("BV","counts_16S"),
         clustering = patient_groups,
         draw_mean_lines=F,col = pal)

@@

barlist( data = rbind(  BV=mM ,
                        counts_16S=xM),
         main = "Monbilicus",
         genes = c("BV","counts_16S"),
         clustering = patient_groups,
         draw_mean_lines=F,col = pal)

barlist( data = rbind(  BV=mG ,
                        counts_16S=xG),
         main = "Gardanerella",
         genes = c("BV","counts_16S"),
         clustering = patient_groups,
         draw_mean_lines=F,col = pal)

@@

shann <- vegan::diversity(t(x),index = c("shannon") )
simp <- vegan::diversity(t(x),index = c("simpson") )
invsimp <- vegan::diversity(t(x),index = c("invsimpson") )
divers <- as.matrix(rbind(shann,simp,invsimp) )
divers[is.infinite(divers)] <- 0
rownames(divers) <- c("Shannon","simpson","Inv Simpson")
barlist( data = divers,
         main = "",
         genes = c("Shannon","simpson","Inv Simpson"),
         clustering = patient_groups,
         draw_mean_lines=F,col = pal)

@@

###################################
# BACTERIAL VAGINOSIS COMPARISSON #
###################################
par(mar=c(4,5,1,12))
temp <- t(t(2^x-1)/colSums(2^x-1))
taxa <- read.csv2("../../../results/taxonomy.csv",row.names = 1,stringsAsFactors = F,as.is = T)
taxa[is.na(taxa)] <- "NA"
taxa <- taxa[rownames(temp),]
temp <- rowsum(temp , taxa$Class)
temp[is.nan(temp)] <- 0
o <- order( rowSums(temp) , decreasing = T)
sample_o <- order( patient_groups )
temp <- temp[o,sample_o]*100
temp <- temp[-grep("NA",rownames(temp)),]
temp <- rbind(temp[1:16,], Other = colSums(temp[17:nrow(temp),]) )
